---
title: "Linear Model"
author: "ChristinaJones"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

# Introduction 

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM Regression 

```{r}
plot(SIMS~ARM,data=data)
```

This scatter plot shows that the greater the pounds of arm force(ARM), the greater the simulation(SIMS)




```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```



```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)


``` 




This scatter plot shows the all the individuals scores and the corresponding ARM and SIMS. The blue line which is the best linear fit to predict what an average SIMS response would be for ARM strength. 
The shaded part is the uncertainty of the blue line. 

```{r}
cor(SIMS~ARM,data=data)
```
This number is the correlation between SIMS and ARM force. Correlation is a measure of the linear association between the two variables.

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation is SIMS = -4.095160 + 0.054563 * ARM 


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")
```
Fit is the predict ARM score when you an ARM force of 88. 
The lwr and upr are the 95% confidence intervals for predicted SIMS scores when the ARM is 88. 

## SIMS~GRIP Regression 

```{r}
plot(SIMS~GRIP,data=data)
```

This scatter plot shows that the greater the pounds of grip strength(GRIP), the greater the simulation(SIMS)



```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

This scatter plot shows the all the individuals scores and the corresponding GRIP and SIMS. The blue line which is the best linear fit to predict what an average SIMS response would be for GRIP strength. 
The shaded part is the uncertainty of the blue line. 



```{r}
cor(SIMS~GRIP,data=data)
```

This number is the correlation between SIMS and GRIP force. Correlation is a measure of the linear association between the two variables.

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
The equation is SIMS = -4.809675 + 0.045463 * GRIP


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.2,newData,interval="prediction")
```
Fit is the predicted SIMS score when the GRIP strength is 94. 

Model 1 (SIMS~ARM)has a slightly higher Residual standard error score of 1.226 while model 2 (SIMS~GRIP) scored 1.22


model 1 (SIMS~ARM) has a higher adjusted R squared score of 0.467 while model 2 (SIMS~GRIP)scored a lower with 0.4053

Model 

## SIMS~ARM+GRIP Regression 


```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
``` 

Model 3 appears to be the better model because the adjusted R squared 

```{r}
cor(SIMS~ARM + GRIP,data=data)
```


## Inferential test 
The is the inferential test to compare models 
This test is an anova 

$H_O$ There is no difference in how well each model fit the data between models  (model1,model2)
$H_A$ There is a difference in how well each model fits th data between models (model1,model2)

```{r}
anova(model.1,model.3)
```

The p value is 0.00004994 which is very low.

We reject the Null hypothesis because the P Value is so low , There is a difference between model1 and model3 ,we have evidence that model3 is better then model1

## MODEL COMPARISONS 
